COVID-19 Cases and Deaths in Canada in 2022 By Region, Age, and Sex

### 2024-12-03 paper/paper.qmd
Updated formatting

---
title: "Number of COVID-19 Cases in Canada in 2022 By Region, Age, and Sex"
subtitle: "Predicting the Factors that Influence the Probability of High Risk of COVID-19"
author: 
  - Bruce Zhang
thanks: "Code and data are available at: [https://github.com/brucejczhang/covid_data](https://github.com/brucejczhang/covid_data)."
date: today
date-format: long
abstract: "This paper examines the demographic and regional factors influencing high-risk classifications for COVID-19 in Canada using logistic regression models, with predictors including age, sex, and region. The analysis reveals that rural regions, males, and specific age intervals exhibit higher probabilities of being classified as high risk, emphasizing disparities in healthcare access and outcomes. These findings highlight the importance of targeted public health interventions, such as resource allocation and vaccination prioritization, to mitigate these risks and can potentially guide interventions for future pandemics. By identifying key predictors and their implications, this study provides a scalable framework for improving pandemic preparedness and understanding health disparities."
format: pdf
toc: true
toc-depth: 3
include-before:
  - \newpage
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-model_region
#| fig-cap: Predicted probability of high risk of COVID-19 by region (Urban vs. Rural). This is a density plot showing that the extremes of predicted probability of high risk are more frequent for both urban and rural regions. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'

@@

```{r}
#| label: fig-model_sex
#| fig-cap: Predicted probability of high risk based on sex. The box-and-whiskers plots show that the median value of the predicted probability of high risk is similar for males and females. There is a large IQR for both. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'

>>>>

---
title: "COVID-19 Cases and Deaths in Canada in 2022 By Region, Age, and Sex"
subtitle: "Predicting the Factors that Influence the Probability of High Risk of COVID-19"
author: 
  - Bruce Zhang
thanks: "Code and data are available at: [https://github.com/brucejczhang/covid_data](https://github.com/brucejczhang/covid_data)."
date: today
date-format: long
abstract: "This paper examines the demographic and regional factors influencing high-risk classifications for COVID-19 in Canada using logistic regression models, with predictors including age, sex, and region. The analysis reveals that rural regions, males, and specific age intervals exhibit higher probabilities of being classified as high risk, emphasizing disparities in healthcare access and outcomes. These findings highlight the importance of targeted public health interventions, such as resource allocation and vaccination prioritization, to mitigate these risks and can potentially guide interventions for future pandemics. By identifying key predictors and their implications, this study provides a scalable framework for improving pandemic preparedness and understanding health disparities."
format: pdf
toc: true
toc-depth: 3
include-before:
  - \newpage
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-model_region
#| fig-cap: Predicted probability of high risk of COVID-19 by region (Urban vs. Rural). The density of probabilities of high risk shows that the extremes of predicted probability of high risk are more frequent for both urban and rural regions. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'

@@

```{r}
#| label: fig-model_sex
#| fig-cap: Predicted probability of high risk based on sex. The median value of the predicted probability of high risk is shown to be similar for males and females. There is a large IQR for both. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'
